Supplementary Material \\

### 2022-01-21 figures/feature-importance/01-ferrenti-approach-PC-v2.tex
Updates from Overleaf

\begin{axis}[
height=1.4222438079424382in,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xlabel={Principal components},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.133808014644924,
ytick style={color=black},
yticklabels={, 0, , 0.1},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:1.4,0.123808014644924);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0779020383908885);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0690715494994265);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0448634890553009);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0396017649392185);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0309892340254588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0286471759268761);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0241373022722755);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0219387724823991);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0191941500093896);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0170987447716404);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0163324377943715);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0142479118996461);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0139471831901937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0125561362477749);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0122752355665442);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0117377683648439);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0108124054147357);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0105912984624588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:19.6,0) rectangle (axis cs:20.4,0.00987028371434172);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:20.6,0) rectangle (axis cs:21.4,0.00946157777094173);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:21.6,0) rectangle (axis cs:22.4,0.00932051055389097);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00851928669553865);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:23.6,0) rectangle (axis cs:24.4,0.00821174057436937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:24.6,0) rectangle (axis cs:25.4,0.00796122578616887);
\addlegendimage{semithick, color=white!53.3333333333333!black};
\addlegendentry{Explained variance};
\end{axis}

>>>>

\begin{axis}[
height=1.6222438079424382in,
legend style={fill opacity=0.8, draw opacity=1, text opacity=1, draw=white!80!black},
tick align=outside,
tick pos=left,
width=3.0444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=26,
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.133808014644924,
ytick style={color=black},
yticklabels={, 0, , 0.1},
title={Explained variance},
legend style={font=\footnotesize},
]
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:0.6,0) rectangle (axis cs:1.4,0.123808014644924);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0779020383908885);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:2.6,0) rectangle (axis cs:3.4,0.0690715494994265);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0448634890553009);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0396017649392185);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0309892340254588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0286471759268761);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:7.6,0) rectangle (axis cs:8.4,0.0241373022722755);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:8.6,0) rectangle (axis cs:9.4,0.0219387724823991);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:9.6,0) rectangle (axis cs:10.4,0.0191941500093896);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:10.6,0) rectangle (axis cs:11.4,0.0170987447716404);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0163324377943715);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0142479118996461);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:13.6,0) rectangle (axis cs:14.4,0.0139471831901937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:14.6,0) rectangle (axis cs:15.4,0.0125561362477749);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:15.6,0) rectangle (axis cs:16.4,0.0122752355665442);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:16.6,0) rectangle (axis cs:17.4,0.0117377683648439);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:17.6,0) rectangle (axis cs:18.4,0.0108124054147357);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:18.6,0) rectangle (axis cs:19.4,0.0105912984624588);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:19.6,0) rectangle (axis cs:20.4,0.00987028371434172);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:20.6,0) rectangle (axis cs:21.4,0.00946157777094173);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:21.6,0) rectangle (axis cs:22.4,0.00932051055389097);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:22.6,0) rectangle (axis cs:23.4,0.00851928669553865);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:23.6,0) rectangle (axis cs:24.4,0.00821174057436937);
\draw[draw=none,fill=white!53.3333333333333!black,fill opacity=0.5] (axis cs:24.6,0) rectangle (axis cs:25.4,0.00796122578616887);
\addlegendimage{semithick, color=white!53.3333333333333!black};
\addlegendentry{Ferrenti approach};
\end{axis}

### 2022-01-21 figures/feature-importance/03-empirical-approach-GB-v2.tex
Updates from Overleaf

\begin{axis}[
height=1.4222438079424382in,
tick align=outside,
tick pos=left,
width=2.8444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xtick style={color=black},
xticklabels={,,},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.941178662009005,
yticklabels={,0,, 0.4,,0.8},
ytick style={color=black},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.871178662009005);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0217568511840037);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.00253604996390695);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0192708196133984);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0198922275506549);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0260375424696281);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0063356815006726);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00319869517406271);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.00540195176007804);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.00695771640251456);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.00312270971606427);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0030932299465922);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0112178627094187);
\path [draw=color0, semithick]
(axis cs:1,0.854956014167526)
--(axis cs:1,0.887401309850484);

@@

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.854956014167526
2 0.00907965200713417
3 -0.000182654889842383
4 0.00923661909617688
5 -0.00820788248180509
6 0.00143690786973603
7 -0.00149882818592621
8 -0.00213482608794717
9 -0.00260933890414728
10 -0.0038254976017747
11 -0.0044786262895489
12 -0.000395131606741384
13 -0.00413997684116445
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.887401309850484
2 0.0344340503608733
3 0.00525475481765629
4 0.0293050201306199
5 0.0479923375831149
6 0.0506381770695201
7 0.0141701911872714
8 0.00853221643607259
9 0.0134132424243034
10 0.0177409304068038
11 0.0107240457216774
12 0.00658159149992578
13 0.0265757022600018
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Gradient boost};
\end{axis}

>>>>

\begin{axis}[
height=1.6222438079424382in,
tick align=outside,
tick pos=left,
width=3.0444876158848764in,
x grid style={white!69.0196078431373!black},
xmajorgrids,
xmin=0.5, xmax=15.5,
xlabel={Principal components},
xtick style={color=black},
y grid style={white!69.0196078431373!black},
ymajorgrids,
ymin=0, ymax=0.941178662009005,
yticklabels={,0,, 0.4,,0.8},
ytick style={color=black},
legend style={font=\footnotesize}
]
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:1.4,0.871178662009005);
\draw[draw=none,fill=color0] (axis cs:1.6,0) rectangle (axis cs:2.4,0.0217568511840037);
\draw[draw=none,fill=color0] (axis cs:2.6,0) rectangle (axis cs:3.4,0.00253604996390695);
\draw[draw=none,fill=color0] (axis cs:3.6,0) rectangle (axis cs:4.4,0.0192708196133984);
\draw[draw=none,fill=color0] (axis cs:4.6,0) rectangle (axis cs:5.4,0.0198922275506549);
\draw[draw=none,fill=color0] (axis cs:5.6,0) rectangle (axis cs:6.4,0.0260375424696281);
\draw[draw=none,fill=color0] (axis cs:6.6,0) rectangle (axis cs:7.4,0.0063356815006726);
\draw[draw=none,fill=color0] (axis cs:7.6,0) rectangle (axis cs:8.4,0.00319869517406271);
\draw[draw=none,fill=color0] (axis cs:8.6,0) rectangle (axis cs:9.4,0.00540195176007804);
\draw[draw=none,fill=color0] (axis cs:9.6,0) rectangle (axis cs:10.4,0.00695771640251456);
\draw[draw=none,fill=color0] (axis cs:10.6,0) rectangle (axis cs:11.4,0.00312270971606427);
\draw[draw=none,fill=color0] (axis cs:11.6,0) rectangle (axis cs:12.4,0.0030932299465922);
\draw[draw=none,fill=color0] (axis cs:12.6,0) rectangle (axis cs:13.4,0.0112178627094187);
\path [draw=color0, semithick]
(axis cs:1,0.854956014167526)
--(axis cs:1,0.887401309850484);

@@

\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.854956014167526
2 0.00907965200713417
3 -0.000182654889842383
4 0.00923661909617688
5 -0.00820788248180509
6 0.00143690786973603
7 -0.00149882818592621
8 -0.00213482608794717
9 -0.00260933890414728
10 -0.0038254976017747
11 -0.0044786262895489
12 -0.000395131606741384
13 -0.00413997684116445
};
\addplot [semithick, color0, mark=-, mark size=4, mark options={solid}, only marks]
table {%
1 0.887401309850484
2 0.0344340503608733
3 0.00525475481765629
4 0.0293050201306199
5 0.0479923375831149
6 0.0506381770695201
7 0.0141701911872714
8 0.00853221643607259
9 0.0134132424243034
10 0.0177409304068038
11 0.0107240457216774
12 0.00658159149992578
13 0.0265757022600018
};
\addlegendimage{semithick, color=color0};
\addlegendentry{Empirical approach};
\end{axis}
